---
title: "Marvel or DC"
output: rmarkdown::github_document
---

## Can we predict whether a given super hero belongs to the Marvel or DC universe based on their super powers?

```{r}
library(dplyr)
library(ggplot2)
library(caret)
library(data.table)

rm(list = ls())
setwd('~/super_heroes')

hero_info = read.csv('heroes_information.csv') %>% 
  mutate(Publisher = factor(Publisher),
         Alignment = factor(Alignment))
hero_powers = read.csv('super_hero_powers.csv', stringsAsFactors = F) %>% 
  mutate(hero_names = as.character(hero_names)) %>% 
  data.table()


hero_powers = as.data.frame(lapply(hero_powers, function(y) gsub("False", 0, y)))
hero_powers = as.data.frame(lapply(hero_powers, function(y) gsub("True", 1, y)))
hero_powers[,2:ncol(hero_powers)] = as.data.frame(lapply(hero_powers[,2:ncol(hero_powers)], 
                                                         function(x) as.numeric(x)))

marvel_dc = hero_info %>% 
  select(name, Publisher, Alignment) %>% 
  filter(Publisher %in% c('Marvel Comics', 'DC Comics')) %>% 
  mutate(Publisher = factor(Publisher)) %>% 
  inner_join(hero_powers, by = c("name" = "hero_names")) %>% 
  filter(Alignment != '-') %>% 
  mutate(Publisher = factor(ifelse(Publisher == 'Marvel Comics', 'marvel', 'dc')))
```

## Control Arguments

10 Fold Cross Validation 

```{r}
#set control arguments
mycontrol = trainControl(method = 'cv',
                         number = 10,
                         classProbs = T,
                         summaryFunction = twoClassSummary,
                         verboseIter = TRUE)
```

## Generalized Linear Model

Using a genarlized linear model with feature selection.

Ridge regression is the best performing model (alpha = 1) with a lambda value of .04 (slightly penalized coefficients)

```{r}
glmnet_model = train(Publisher ~ .,
                     marvel_dc %>% select(-name),
                     method = 'glmnet',
                     trControl = mycontrol,
                     tuneGrid = expand.grid(alpha = 0:1, 
                                            lambda = seq(0, .05, by = .01)))
plot(glmnet_model)
```

## Testing the Results of the Model

Our model tends to err on the side of predicting a super hero to belong to Marvel comics over DC comics. 

* Sensitivity - 29% - percent of DC super heroes correctly predicted to be DC comics

* Specificity - 96% - percent of Marvel super heroes correctly predicted to belong to Marvel Comics

* Pos Pred value - 82% - percent of predicted DC super heroes  that actually belonged to DC

* Neg Pred Value - 70% - percent of predicted marvel heroes that actually belonged to Marvel. 

If our model predicts that a given super hero belongs to DC comics, there's a pretty good likely hood that it is actually the case. 

If our model predicts that a super hero belongs to Marvel, there is a higher chance of misclassification error. 

```{r}
confusionMatrix(predict(glmnet_model, marvel_dc), marvel_dc$Publisher)
```

